The Impact of Accretion Disk Winds on the Optical Spectra of Cataclysmic Variables

### 2015-01-21 draft.tex
trimmed
figure order
commit before fiddling with sobolev things

The poloidal (non-rotational) velocity field of the wind, $v_l$, is given by
\begin{equation}
v_l=v_0+\left[v_{\infty}(r_0)-v_0\right]\frac{\left(l/R_v\right)^{\alpha}}{\left(l/R_v\right)^{\alpha}+1},
\label{v_law}
\end{equation}
where $l$ is the poloidal distance along a particular wind
streamline. The terminal velocity along a streamline, $v_{\infty}$, is
set to a fixed multiple of the escape velocity at the launch
point. The launch velocity from the disk surface, $v_0$, is assumed to
be constant (set to $6$~km~s$^{-1}$). Once the wind is launched, it
accelerates, reaching half of its terminal velocity at $l = R_v$. The
velocity law exponent $\alpha$ controls how quickly the wind
accelerates. Larger values of $\alpha$ cause the main region of 
acceleration to occur close to $R_v$, whereas smaller values
correspond to fast acceleration close to the disk (see
Fig.~\ref{acc_law}). The rotational velocity $v_\phi$ is originally 
Keplerian and is assumed to conserve its specific angular momentum
such that
\begin{equation}
v_\phi r = v_{k} r_0,
\label{v_law}
\end{equation}
where $v_{k}=(GM_{WD}/r_0)^{1/2}$.

@@

\begin{table}
\centering
\begin{tabular}{p{2cm}p{2cm}p{2cm}}
Model Parameters \\
\hline Parameter 	&	 Model A  & Model B \\ 
\hline \hline 
$M_{WD}$ 	 &	 $0.8~M_{\odot}$  &     \\ 
$R_{WD}$ 	 &	 $7\times10^{8}$~cm  & \\ 
$T_{WD}$ 	 &	 $40,000$~K        &  \\
$M_{2}$ 	& -&	 $0.6~M_{\odot}$   \\ 
$q$ 	&- &	 $0.75$   \\ 
$P_{orb}$ 	&- &	 $5.57$~hr   \\ 
$a$ 	& -&	 $194.4~R_{WD}$   \\ 
$R_2$   &   -  &	 $69.0~R_{WD}$  \\ 
$\dot{M}_{acc}$ 	 &	 $10^{-8}~M_{\odot}yr^{-1}$  &\\ 
$\dot{M}_{wind}$  &	$10^{-9}~M_{\odot}yr^{-1}$å  & \\ 
$r_{min}$ 	&	 $4~R_{WD}$ &  \\ 
$r_{max}$ 	&	 $12~R_{WD}$  &  \\ 
$r_{disk} (max)$ 	&	 $34~R_{WD}$  &  \\ 
$\theta_{min}$ 	&	 $20.0^{\circ}$  &  \\ 
$\theta_{max}$ 	&	 $65.0^{\circ}$  &  \\ 
$\gamma$ 	&	 $1$  &  \\ 
$v_{\infty}$ 	&	 $3~v_{esc}$  &  \\ 
$R_v$ 	        &	 $100~R_{WD}$  &  $142.9~R_{WD}$  \\ 
$\alpha$ 	&	 $1.5$   &   $4$\\
\end{tabular}
\centering
\caption{
Parameters used for the geometry and kinematics of the benchmark 
CV model (model A), which is optimized for the UV band, and a model
which is optimized for the optical band and described in section 5 (model B).
For model B, only parameters which are altered are given - otherwise the
model A parameter is used. $P_{orb}$ is the orbital period 
(the value for RW Tri from ?? is adopted, see section 5.4) and 
$R_2$ is the radius of a sphere with the volume of the secondary's Roche lobe. 
Other quantities are defined in the text or Fig.~\ref{cartoon}.
Secondary star parameters are only quoted for 
model B as we do not show eclipses with the 
benchmark model (see section 5.4).
}
\label{wind_param}
\label{modelb_table}
\end{table}

@@

\begin{figure} 
\includegraphics[width=0.5\textwidth]{figures/modela_escaping.eps}
\caption{Total packet-binned spectra across all viewing angles. 
The thick black line shows the total 
integrated escaping spectrum, 
while the green line shows disk photons which escape without being reprocessed by
the wind. The red line show the contributions from reprocessed photons. 
Recombination continuum emission blueward of the Balmer 
edge is already prominent relative to other wind continuum processes, but is not sufficient
to fill in the Balmer jump in this specific model}
\label{cont}
\end{figure}

@@

The emission measure of a plasma is directly proportional to its density.
The simplest way to simultaneously affect the density in the wind (for fixed mass loss rate)
as well as the velocity gradients is by modifying the poloidal velocity
law. We have therefore conducted a exploratory sensitivity study in
which we focus on just two kinematic variables (section~\ref{kinematics}):

@@

\begin{figure} 
\includegraphics[width=0.5\textwidth]{figures/modelb_escaping.eps}
\caption{Total packet-binned spectra across all viewing angles. 
The thick black line shows the total 
integrated escaping spectrum, 
while the green line shows disk photons which escape without being reprocessed by
the wind. The red line show the contributions from reprocessed 
photons. 
In this denser model the reprocessed contribution is significant compared
to the escaping disk spectrum. The Balmer continuum emission is prominent, and
the wind has a clear effect on the overall spectral shape.}
\label{modelb_escape}
\end{figure}

@@

>>>>

The poloidal (non-rotational) velocity field of the wind, $v_l$, is given by
\begin{equation}
v_l=v_0+\left[v_{\infty}(r_0)-v_0\right]\frac{\left(l/R_v\right)^{\alpha}}{\left(l/R_v\right)^{\alpha}+1},
\label{v_law}
\end{equation}
where $l$ is the poloidal distance along a particular wind
streamline. The terminal velocity along a streamline, $v_{\infty}$, is
set to a fixed multiple of $v_{esc}$, the escape velocity at the launch
point. The launch velocity from the disk surface, $v_0$, is assumed to
be constant (set to $6$~km~s$^{-1}$). Once the wind is launched, it
accelerates, reaching half of its terminal velocity at $l = R_v$. The
velocity law exponent $\alpha$ controls how quickly the wind
accelerates. Larger values of $\alpha$ cause the main region of 
acceleration to occur close to $R_v$, whereas smaller values
correspond to fast acceleration close to the disk (see
Fig.~\ref{acc_law}). The rotational velocity $v_\phi$ is originally 
Keplerian and is assumed to conserve its specific angular momentum
such that
\begin{equation}
v_\phi r = v_{k} r_0,
\label{v_law}
\end{equation}
where $v_{k}=(GM_{WD}/r_0)^{1/2}$.

@@

\begin{table}
\centering
\begin{tabular}{p{2cm}p{2cm}p{2cm}}
Model Parameters \\
\hline Parameter 	&	 Model A  & Model B \\ 
\hline \hline 
$M_{WD}$ 	 &	 $0.8~M_{\odot}$  &     \\ 
$R_{WD}$ 	 &	 $7\times10^{8}$~cm  & \\ 
$T_{WD}$ 	 &	 $40,000$~K        &  \\
$M_{2}$ 	& -&	 $0.6~M_{\odot}$   \\ 
$q$ 	&- &	 $0.75$   \\ 
$P_{orb}$ 	&- &	 $5.57$~hr   \\ 
$a$ 	& -&	 $194.4~R_{WD}$   \\ 
$R_2$   &   -  &	 $69.0~R_{WD}$  \\ 
$\dot{M}_{acc}$ 	 &	 $10^{-8}~M_{\odot}yr^{-1}$  &\\ 
$\dot{M}_{wind}$  &	$10^{-9}~M_{\odot}yr^{-1}$å  & \\ 
$r_{min}$ 	&	 $4~R_{WD}$ &  \\ 
$r_{max}$ 	&	 $12~R_{WD}$  &  \\ 
$r_{disk} (max)$ 	&	 $34~R_{WD}$  &  \\ 
$\theta_{min}$ 	&	 $20.0^{\circ}$  &  \\ 
$\theta_{max}$ 	&	 $65.0^{\circ}$  &  \\ 
$\gamma$ 	&	 $1$  &  \\ 
$v_{\infty}$ 	&	 $3~v_{esc}$  &  \\ 
$R_v$ 	        &	 $100~R_{WD}$  &  $142.9~R_{WD}$  \\ 
$\alpha$ 	&	 $1.5$   &   $4$\\
\end{tabular}
\centering
\caption{
Parameters used for the geometry and kinematics of the benchmark 
CV model (model A), which is optimized for the UV band, and a model
which is optimized for the optical band and described in section 5 (model B).
For model B, only parameters which are altered are given - otherwise the
model A parameter is used. $P_{orb}$ is the orbital period 
(the value for RW Tri from Walker 1963 is adopted, see section 5.4) and 
$R_2$ is the radius of a sphere with the volume of the secondary's Roche lobe. 
Other quantities are defined in the text or Fig.~\ref{cartoon}.
Secondary star parameters are only quoted for 
model B as we do not show eclipses with the 
benchmark model (see section 5.4).
}
\label{wind_param}
\label{modelb_table}
\end{table}

\nocite{walker1963}

@@

\begin{figure} 
\includegraphics[width=0.45\textwidth]{figures/modela_escaping.eps}
\caption{Total packet-binned spectra across all viewing angles. 
The thick black line shows the total 
integrated escaping spectrum, 
while the green line shows disk photons which escape without being reprocessed by
the wind. The red line show the contributions from reprocessed photons. 
Recombination continuum emission blueward of the Balmer 
edge is already prominent relative to other wind continuum processes, but is not sufficient
to fill in the Balmer jump in this specific model}
\label{cont}
\end{figure}

@@

The emission measure of a plasma is directly proportional to its density.
The simplest way to simultaneously affect the density in the wind (for fixed mass loss rate)
as well as the velocity gradients is by modifying the poloidal velocity
law. To do this, we focus on just two kinematic variables (section~\ref{kinematics}):

@@

@@

\begin{figure} 
\includegraphics[width=0.45\textwidth]{figures/modelb_escaping.eps}
\caption{Total packet-binned spectra across all viewing angles. 
The thick black line shows the total 
integrated escaping spectrum, 
while the green line shows disk photons which escape without being reprocessed by
the wind. The red line show the contributions from reprocessed 
photons. 
In this denser model the reprocessed contribution is significant compared
to the escaping disk spectrum. The Balmer continuum emission is prominent, and
the wind has a clear effect on the overall spectral shape.}
\label{modelb_escape}
\end{figure}
